---
title: "Ryan Tillis - Developing Data Products - Data Science - Quiz 3 - Coursera"
author: <a href="http://www.ryantillis.com"> Ryan Tillis </a>
date: "August 11, 2016"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Developing Data Products Quiz 3

This is Quiz 3 from the Developing Data Products course within the Data Science Specialization. This publication is intended as a learning resource, all answers are documented and explained.

###Questions
<hr>
<font size="+2">1.  </font> WWhich of the following items is required for an R package to pass R CMD check without any warnings or errors?

<hr>

<font size="+1">
<b>

* An explicit software license

</b>
</font>

<hr>

```{r Question 1}

```

<hr>

<font size="+2">2.  </font> Which of the following is a generic function in a fresh installation of R, with only the default packages loaded? (Select all that apply)

<hr>

<font size="+1">
<b>

* show

* mean

* predict

</b>
</font>

<hr>

<font size="+2">3.  </font> What function is used to obtain the function body for an S4 method function?

<hr>

<font size="+1"> 
<b>

* getMethod()

</b>

</font>

<hr>
```{r Question 3c}

```

<hr>

<font size="+2">4.  </font> Please download the R package DDPQuiz3 from the course web site. Examine the ğšŒğš›ğšğšŠğšğšğš–ğšğšŠğš— function implemented in the R/ sub-directory. What is the appropriate text to place above the ğšŒğš›ğšğšŠğšğšğš–ğšğšŠğš— function for Roxygen2 to create a complete help file?

<hr>

<font size="+1">
<b>
```{R last}
#' This function calculates the mean
#' 
#' @param x is a numeric vector
#' @return the mean of x
#' @export
#' @examples 
#' x <- 1:10
#' createmean(x)
```

</b>
</font>

<hr>

Check out my website at: <http://www.ryantillis.com/>

<hr>
